---
title: "Jurimetrics"
date: "Brussels, July 06"
author: 
- "José de Jesus Filho"
- "Julio Trecenti"
- "Brazilian Jurimetrics Association"
output: revealjs::revealjs_presentation
---

<!-- Slide 01 ----------------------------------------------------------------->
## What is jurimetrics?

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

- Statistics in the law
- Jurimetrics Brazilian Association

<!-- Slide 02 ----------------------------------------------------------------->
## Jurimetrics: spheres

- One litigation
    - Compensating for the loss of a chance
- Many litigations
    - Predictive models
    - Decision making
    - Topic models
- Public policy
    - Public policy impact
- Court administration
    - litigation complecity
    - court productivity

<!-- Slide 03 ----------------------------------------------------------------->
## Orgs

- github.com/abjur: ABJ's org
- github.com/courtsbr: github organisation
- github.com/decryptr: breaking captchas using R

<!-- Slide 04 ----------------------------------------------------------------->
## Packages

- `tjsp` and `esaj` packages: web scraping.
- `jurisMiner`: analyze judicial text data.
- ...

<!-- Slide 05 ----------------------------------------------------------------->
## Download: usage

```{r eval=FALSE}
library(tjsp)
s <- cjsg_session()
parms <- cjsg_parms(s, livre = 'erro medico')
cjsg(s, parms, path = 'data-raw', max_pag = 10)
```

<!-- Slide 06 ----------------------------------------------------------------->
## Parsing: usage

```{r eval=FALSE}
files <- dir('data-raw', full.names = TRUE)
d_cjsg <- parse_cjsg(files)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# saveRDS(d_cjsg, 'data-raw/d_cjsg.rds')
library(magrittr)
d_cjsg <- readRDS('data-raw/d_cjsg.rds')
```

```{r}
dplyr::glimpse(d_cjsg)
```

<!-- Slide 07 ----------------------------------------------------------------->
## Download and parse full decision

```{r}
code <- d_cjsg$cd_acordao[1]
tjsp::download_pdf(code, 'data-raw')
```

<!-- Slide 07 ----------------------------------------------------------------->
## Clean text data

<!-- Slide 08 ----------------------------------------------------------------->
## Topic models

- unsupervised learning of litigation topics

<!-- Slide 09 ----------------------------------------------------------------->
## Predictive models

- using bag of words + LASSO, RF, NN etc.

<!-- Slide 10 ----------------------------------------------------------------->
## Influence diagrams -> decision

- bayesian network with decision node.

<!-- Slide 11 ----------------------------------------------------------------->

```{r eval=FALSE}
u_img <- "http://esaj.tjsp.jus.br/cjsg/imagemCaptcha.do"
u_aud <- "http://esaj.tjsp.jus.br/cjsg/somCaptcha.do"
r_img <- httr::GET(u_img, httr::write_disk('data-raw/captcha.png'))
r_aud <- httr::GET(u_aud, httr::write_disk('data-raw/captcha.mp3'))
```
<!-- Slide 12 ----------------------------------------------------------------->
## Breaking captchas

```{r fig.height=3}
library(decryptr)
read_captcha('data-raw/captcha.png') %>% plot()
captchaSajAudio::decifrar('data-raw/captcha.mp3')
```

<!-- Slide 13 ----------------------------------------------------------------->
## Future work: tech

- Better scrapers
- Public API

<!-- Slide 14 ----------------------------------------------------------------->
## Future work: research

- Most important arguments

<!-- Slide 15 ----------------------------------------------------------------->
## Links